Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
to-do items for paradigm section

Section explains space of measures to explore, mean-normalization

\begin{itemize}
\item \sout{one challenge of metric-evaluation: underlying doc difficulty }
  \begin{itemize}
  \item \sout{describe mean-subtraction}
  \end{itemize}
\end{itemize}
When considering a candidate measure $m$, reporting correlations of
$m$ with absolute HTER scores can conflate $m$'s power in identifying
which of two candidate translations is better with $m$'s (and HTER)'s
ability to distinguish which of two source documents is more difficult
to translate. To avoid this conflation, we consider the mean-removed
$m$ and HTER scores; this lowers the correlations but ensures that the
reported correlations are among differences in the translations rather
than among differences in the underlying document.

>>>>

\subsection{Reference evaluation measures}

TO DO: TALK ABOUT HUMAN F/A JUDGMENTS

When considering a candidate measure $m$, reporting correlations of
$m$ with absolute HTER scores can conflate $m$'s power in identifying
which of two candidate translations is better with $m$'s (and HTER)'s
ability to distinguish which of two source documents is more difficult
to translate. To avoid this conflation, we consider the mean-removed
$m$ and HTER scores; this lowers the correlations but ensures that the
reported correlations are among differences in the translations rather
than among differences in the underlying document.

TO DO: MENTION DELTAS IN A FOOTNOTE, AND CITE MetricsMATR SYSTEM PAPER
